---
title: "Assignment B2"
output: github_document
date: "2024-10-29"
---
# Assignment B2

In this assignment I will practice making my own R package.

## Exercise 1: Function(s)
For this exercise I need to render the documentation for my function in the package. I have chosen to use the same function I submitted for assignment B1. 

First I will load the packages that I will need to use in this assignment.

```{r}
library(gapminder)
library(roxygen2)
library(devtools)
library(usethis)
library(testthat)
```

Now I will render the documentation for my function in the package. 
#' @title Calculate the coefficient of variation

#' @description This calculates the coefficient of variation (standard deviation divded by the mean) to assess variability in the dataset. 

#' @param .x. The variable of interest we use from the dataset to calculate the coefficient of variation. I am using the label "x" to represent the variable of interest. I also chose to use "x" as this is common notation used in field of statistics.
#' @param .na.rm. This is a logical argument used to ensure that any missing values (NA) are removed from the dataset. I have used the label na.arm as this is the common label used in this field when defining what to do when there is missing data (i.e., NAs) in the dataset. 

#' @return A numeric value is returned that tells us what the coefficient of variation is. 

#' @examples
#' # Example 1: Basic use with a numeric vector
#' data <- c(10, 20, 30, 40, 50)
#' cv_function(data)
#' 
#' # Example 3: Basic use with a numeric vector again
#' data <- c(100, 63, 4.5, 17.75, 13)
#' cv_function(data)
#' 
#' # Example 3: Basic use with a numeric vector again
#' data <- c(3.5, 8, 6.5, 2, 14.5)
#' cv_function(data)

#' @export
```{r}
cv_function <- function(x, na.rm = TRUE) {
  if (!is.numeric(x)) {
    stop("Input must be numeric")
  }
  mean_value <- mean(x, na.rm = na.rm) 
  sd_value <- stats::sd(x, na.rm = na.rm)
  return((sd_value / mean_value) * 100)
}
```

I created a new file named cv and saved this function to the R/ folder in my cv package. I then ran document() in the console to create the .Rd help file in the man/ folder. I can test that everything is working properly by running the following chunk of code.

```{r}
?cv_function
```

This produces the correct documentation with my roxygen2 tags showing all of the information. 

Lastly, I want to connect this package to github using the follow chunk of code.

## Exercise 2: High Level Documentation 
I will create a README Rmd file where I will write out the package description, installation instructions, and demonstrated usage.  

```{r}
#generate a README file#
use_readme_rmd()
```
As an example, the code used to create the README file is included above. 

## Exercise 3: DESCRIPTION FILE

Now I will finish filling out the description file. I already have the title and short description listed. I have also picked a license by running use_mit_license("Jessie Chan"). 

I updated the version number so that it reflects the correct version and after that, my description file is complete. Next, I added in dependencies by putting an "imports" section in the description and listing out the packages I want to import. These were the gapminder package and stats package.  To illustrate some calls from external packages I called from the stats package, which means I changed the code in my function from just sd to stats::sd to illustrate I understand how to do this. After this I ran the devtools::document() function to save everything.

## Exercise 4: Tests

For the final exercise, I will install unit tests into my package. First, I will create a test file (use_testthat()), create a file (use_test("cv_function")), and then copy the tests I used for assignment B1 into this folder. After my tests have been copied I will run devtools::test() to ensure my tests still pass. 
